\Large{Research Seminar Software Science} \\ \huge{Simulation of monadic effects in Haskell}

### 2018-06-25 paper.tex
changed putInStore in papeer and removed getStore from code

    \noindent The \textbf{putInStore} function is taking a \textit{Variable} and a \textit{Store} to then return a tuple containing an Exception data type and the \textit{Store} (modified or not). The Exception data either raises an \textit{Exception} or returns a \textit{Variable}. The \textbf{case of} construct is used taking the result of a filter being applied to the \textit{Store}. The filter will check if the \textit{Store} contains the \textit{Variable} provided as an input in the \textbf{putInStore} function. This look up is done on the name of the \textit{Variable} which is achieved by applying the function \textbf{getVarName} to the \textit{Variable}. The implementation of the \textbf{getVarName} follows below:

@@

>>>>

    \noindent The \textbf{putInStore} function is taking a \textit{Variable} and a \textit{Store} to then return a tuple containing an Exception data type and the \textit{Store} (modified or not). The Exception data either raises an \textit{Exception} or returns a \textit{Variable}. The \textbf{case of} construct is used taking the result of a filter being applied to the \textit{Store}. The filter will check if the \textit{Store} contains the \textit{Variable} provided as an input in the \textbf{putInStore} function. This look up is done on the name of the \textit{Variable} which is achieved by applying the function \textbf{getVarName} to the \textit{Variable}. If the check would be performed directly on the \textit{Variable} type then the filter will produce unwanted behavior and allow \textit{Variable} in the following example to be placed in the \textit{Store}. 
    \begin{center}
            \textbf{ghci$>$} putInStore \textcolor{red}{(IntVar ``a" 5)} \textcolor{green}{ $\big[$ IntVar "a" 6 $\big]$} \\
             (Return (IntVar ``a" 5),\textcolor{green}{$\big[$IntVar ``a" 5, IntVar ``a" 6$\big]$})
        \end{center}

    \noindent This is not the behavior that it is desired since the store now contains two identical variable names with different values. Consequently, the implementation of the \textbf{getVarName} follows below:

@@

    \begin{tcolorbox}
    \begin{lstlisting}[language=Haskell] 
    getFromStore      :: String -> StateMonad (Exceptions Variable)
    getFromStore name = getStore `bindS` \store -> 
     case (filter (\v -> getVarName v == name ) store) of 
       []  -> returnS (raise ("variable " ++ name ++ " does not exist"))
    (x:xs) -> returnS (returnE x)

    \noindent The \textbf{getFromStore} function is taking the name of the variable as a \textit{String} and a \textit{Store} to then return a tuple containing an Exception data type and the \textit{Store} (modified or not).
